Bayesian Sparsification of Deep $\cplx$-valued networks

### 2020-03-18 paper/paper.tex
repalced textwidth with columnwidth; used LaTeX builtin appendix command
Some minor changes * proper citation for ARD prior (Neal, 1996); added sums to kl-div * use rv-pipe-par notation, to emphasize conditional dependence * reverted to sections in appendix

% Binary dropout with rate $p \in (0, 1)$ uses $
%   p_\xi
%     = \mathcal{B}\bigl(
%       \{0, \tfrac1{1-p}\}, 1-p
%     \bigr)
% $, whereas in Gaussian dropout $
%   \xi \sim \mathcal{N}(1, \alpha)
% $ for $\alpha = \tfrac{p}{1-p}$.
% This suggests making $\alpha$ a variational parameter
% and optimizing it in \eqref{eq:elbo_general} with an appropriate penalty term. Thus,
%
Variational Dropout assumes fully factorized Gaussian approximate posterior $
  q_\theta(\omega)
    = \prod_j \mathcal{N}(\mu_j, \alpha_j \mu_j^2)
$ and factorized log-uniform prior $\pi(\omega)$ with $
  \pi(\omega_j) \propto \lvert \omega_j \rvert^{-1}
$. The divergence term in \eqref{eq:elbo} unravels into a sum of the following
analytically intractable terms:
\begin{equation}  \label{eq:improper-kl-div-real}
  KL(q_\theta \| \pi)
    \propto
      \frac12 \mathbb{E}_{\varepsilon \sim \mathcal{N}(0, 1)}
        \log{\Bigl\lvert \tfrac1{\sqrt{\alpha}} + \varepsilon \Bigr\rvert^2}
      % \frac12 \mathbb{E}_{\varepsilon \sim \mathcal{N}(0, 1)}
      %   \log{\bigl\lvert 1 + \sqrt{\alpha} \varepsilon \bigr\rvert^2}
      % - \frac12 \log{\alpha}
  \,.
\end{equation}
\citet{kingma_variational_2015} approximate this expression by a non-linear polynomial
regression over $\alpha \in (0, 1)$. \citet{molchanov_variational_2017} refine the
approximation by using a nonlinear regression based on sigmoid and soft-plus.
% see p.6 sec 3.4 of kingma_variational_2015
In appendix~\ref{sub:real-chisq-grad} we verify the value and the derivative of their
approximation against the Monte-Carlo estimate of \eqref{eq:improper-kl-div-real} for $\alpha$
varying over a fine logarithmic grid and the gradient of \eqref{eq:improper-kl-div-real},
for which we obtain an exact expression.
% (!) good for SGVB: gradient-based methods require unbiased gradient estimates
%
% (in) it is in poor taste to brag about this begin the first time anyone has derived a
% derivative of an intractable function.
The key role in the factorization is played by $\alpha_j$, which reflects the relevance
of the parameter $\omega_j$ it is associated to, by being the ratio of its squared mean
to its variance. Thus, \citet{molchanov_variational_2017} focus on the model sparsification
capabilities of Variational Dropout, optimizing $\alpha$ for each individual parameter.
\citet{kharitonov_variational_2018} address theoretical issues with improper priors and
propose an alternative Bayesian Dropout method based on \textit{Automatic Relevance
Determination} procedure. In essence, the log-uniform factor $\pi(\omega_{ij})$ is replaced by
a proper ARD Gaussian prior $
  \mathcal{N}(0, \tau^{-1}_{ij})
$ with learnable precision $\tau_{ij} > 0$. This method, known as \textit{Empirical Bayes},
fits a prior distribution while performing Variational Inference. Maximizing \eqref{eq:elbo}
over $\tau$, holding other parameters fixed, yields $
  \tau^* = {(\mu^2 + \sigma^2)}^{-1}
$, whence
\begin{equation}  \label{eq:ard-kl-div-real}
  KL(q_\theta \| \pi)
    = \tfrac12 \log{\bigl(1 + \tfrac1{\alpha} \bigr)}
    \,.
\end{equation}
Flexibility in specification of $q_\theta$ enables developing structured dropout with
shared $\alpha$ across groups of parameters $\omega$.

Another contribution of \citep{kingma_variational_2015} is the analysis of the effects of the
\textit{local reparameterization trick} on the variance of the gradient of \eqref{eq:elbo}.
Proposed by \citet{wang_fast_2013} to speed up Gaussian dropout, this trick translates
uncertainty from parameters of the model to intermediate outputs within the network:
the stochasticity of $
  W \sim \prod_{ij} \mathcal{N}(\mu_{ij}, \alpha_{ij} \mu_{ij}^2)
$ in a linear layer $
  y = b + W^\top x
$ with $
  W \in \mathbb{R}^{n\times m}
$ is pushed to its output
\begin{equation}  \label{eq:r-gauss-trick}
    y \sim \prod_i \mathcal{N}\Bigl(
          b_i + \sum_j \mu_{ij} x_j,
          \sum_j \alpha_{ij} \mu_{ij}^2 x_j^2
      \Bigr)
    \,.
\end{equation}
%
\citet{kingma_variational_2015} show, that for the case of fully factorized Gaussian
posterior approximations, using \eqref{eq:r-gauss-trick} decorrelates the estimators
\eqref{eq:elbo} within the mini-batch and makes the gradient estimator $
  \nabla_\theta \tilde{\mathcal{L}}
$ more statistically efficient. Specifically for the problem of selecting relevant parameters
\citet{molchanov_variational_2017} further improve the efficiency of the estimator of the $
  \nabla_\mu \tilde{\mathcal{L}}
$ by introducing \textit{additive noise parameterization}. They revert the $(\mu, \alpha)$
parameterization back to the equivalent $(\mu, \sigma^2)$, since it stabilizes gradients
of SGVB \eqref{eq:elbo}, by rendering the gradient with respect to $\mu$ independent from
the local output noise, injected by \eqref{eq:r-gauss-trick}. The relevance $\alpha$ is
calculated using the ratio $
  \tfrac{\sigma^2}{\mu^2}
$ when needed in the divergence term.

@@

The $\cplx$-variant of the local reparameterization trick utilizes the fact that Gaussian
vectors are closed under affine transformations:
% $\cplx$-Gaussians are closed under affine transformations
\begin{equation}  \label{eq:cn-affine}
  b + A z \sim \mathcal{N}_n^{\cplx}\bigl(
      b + A\mu, A \Gamma A^{\hop}, A C A^\top
    \bigr)
  \,,
\end{equation}
for $A \in \cplx^{n \times m}$ and $b \in \cplx^{n}$. Therefore, if $W \in \cplx^{n\times m}$
is drawn from a fully factorized approximation
\begin{equation}  \label{eq:c-gauss-vi-general}
  W \sim q(W)
    = \prod_{ij} \mathcal{N}^{\cplx} \bigl(
      \mu_{ij}, \Sigma_{ij}, C_{ij}
    \bigr)
  \,,
\end{equation}
with $
  \mu, C \in \cplx^{n\times m}
$, $\Sigma \in \real^{n\times m}$, and $
  \lvert C_{ij} \rvert^2 \leq \Sigma_{ij}
$, then for $x \in \cplx^m$ and $b \in \cplx^n$ the vector $y = b + W x$ has independent
components with
\begin{equation}  \label{eq:cplx-gauss-trick}
  y_i
    \sim \mathcal{N}^{\cplx}
      \Bigl(
        % e_i^\top \mu x + b_i,
        b_i + \sum_{j=1}^m \mu_{ij} x_j,
        \, \sum_{j=1}^m \Sigma_{ij} \lvert x_j \rvert^2,
        \, \sum_{j=1}^m C_{ij} x_j^2
      \Bigr)
    \,.
\end{equation}
The trick requires three operations, i.e. $b + \mu x$, $\Sigma \lvert x \rvert^2$ and
$C x^2$ with the complex modulus and square applied elementwise, and can be applied to
any layer, the output of which depends linearly on its parameters, such as convolutional,
affine, and bilinear transformations ($
  (x, z) \mapsto x^\top W^{(j)} z + b_j
$). Similar to $\real$ case, Variational Dropout for $\cplx$ convolutions draws independent
realizations of $W$ for each spatial patch in the input \citep{molchanov_variational_2017}.
This provides faster computations and better statistical efficiency of the SGVB gradient
estimator stemming from decorrelated gradient estimates from overlapping patches
\citep{kingma_variational_2015}, allowing \eqref{eq:cplx-gauss-trick} to leverage $\cplx$
convolutions of the relation and variance kernels with elementwise complex squares $x^2$
and amplitudes $\lvert x \rvert^2$.
% Weight sharing is essentially pushed to shared variational parameters $\theta$ in the approximation $q_\theta$.
% A convolution is a matrix product of $W$, unrolled into a toeplitz matrix, and im-to-col
% flattened intput $x$

@@

\begin{figure}[!t]
  \centering
  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=\columnwidth]{figure__musicnet__threshold.pdf}
  \end{subfigure}
  \caption{%
    Test split performance and compression rate for a $\cplx$-valued net on MusicNet.
  }
  \label{fig:hist__and__threshold__tradeoff}
\end{figure}

@@

Shaded horizontal bands reflect the spread of the performance of the uncompressed network
after ``dense'' stage. Each point represents a precision-compression value attained by the
network after ``fine-tune'' stage. The end of each point's tail represents the performance
gain or loss from running the ``fine-tune'' stage.
%
We make a couple of observations based on the results of these plots. First, \texttt{fft}
features perform on par with raw colour channel data in the convolutional networks across most
compression rates, but require high compression rate to make wide shallow dense network work
as well. The upward trend manifests itself in MNIST and Fashion MNIST experiments as well
(see appendix~\ref{sub:mnist_like_experiments}). Finally, overall $\cplx$ variational dropout
methods seem to compress networks adequately well without much loss in performance.

% a couple of plots from MNIST and Fashion-MNIST
\begin{figure}[!t]
  \centering
  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
    \centering
    % \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/legacy__VD__fashionmnist__fft__-0.5.pdf}
    \includegraphics[width=0.8\columnwidth]{figure__mnist-like__trade-off/legacy__VD__kmnist__fft__-0.5.pdf}
    % \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/VD__kmnist__fft__-0.5.pdf}
  \end{subfigure} \\%
  % \hfill
  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
    \centering
    % \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/legacy__VD__fashionmnist__raw__-0.5.pdf}
    \includegraphics[width=0.8\columnwidth]{figure__mnist-like__trade-off/legacy__VD__kmnist__raw__-0.5.pdf}
    % \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/VD__kmnist__raw__-0.5.pdf}
  \end{subfigure} \\%
  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
    \centering
    % \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/legacy__VD__mnist__fft__-0.5.pdf}
    \includegraphics[width=0.8\columnwidth]{figure__mnist-like__trade-off/legacy__VD__emnist_letters__fft__-0.5.pdf}
    % \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/ARD__kmnist__fft__-0.5.pdf}
  \end{subfigure} \\%
  % \hfill
  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
    \centering
    % \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/legacy__VD__mnist__raw__-0.5.pdf}
    \includegraphics[width=0.8\columnwidth]{figure__mnist-like__trade-off/legacy__VD__emnist_letters__raw__-0.5.pdf}
    % \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/VD__emnist_letters__raw__-0.5.pdf}
  \end{subfigure}
  \caption{%
    The compression-accuracy trade-off on KMNIST and the letters of the Extended MNIST datasets.
    (\textit{top}) \texttt{fft} features, (\textit{bottom}) \texttt{raw} features.
  }
  \label{fig:mnist-like__trade-off}
\end{figure}

@@

% compare compressed cplx-vgg against real-vgg
\begin{figure}[!t]
  \centering
  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=\columnwidth]{figure__cifar__trade-off/legacy__augmentedcifar10__raw__-0.5.pdf}
  \end{subfigure}
  \caption{%
    Compression-accuracy frontier for $\real$ and $\tfrac12 \cplx$ versions of VGG16 on CIFAR10.
  }
  \label{fig:figure__cifar10__trade-off}
\end{figure}

@@

\begin{figure}[!h]
  \centering
  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=\columnwidth]{figure__musicnet__trade-off/paper__musicnetram__fft__-0.5.pdf}
  \end{subfigure}
  \caption{%
    Performance-compression trade-off using \textbf{\color{blue} VD} and \textbf{\color{orange} ARD}.
    The \textbf{\color{pink} version} of the network with kernel $3$ in the first convolution is
    compressed with VD only.
  }
  \label{fig:musicnet__trade-off}
\end{figure}

@@

@@

\section{Appendix} % (fold)
\label{sec:appendix}

\subsection{Complex-valued local reparameterization} % (fold)
\label{sub:complex_valued_local_reparameterization}

@@

% subsection complex_valued_local_reparameterization (end)

\subsection{Gradient of the KL-divergence in $\real$ case} % (fold)
\label{sub:real-chisq-grad}  % gradient_of_the_kl_divergence_in_R_case

@@

% subsection real-chisq-grad (end)

\subsection{MNIST-like experiments} % (fold)
\label{sub:mnist_like_experiments}

@@

% subsection mnist_like_experiments (end)

@@

\subsection{CIFAR10 experiments} % (fold)
\label{sub:cifar_experiments}

@@

% subsection cifar_experiments (end)

\subsection{Backpropagation through $\cplx$-networks} % (fold)
\label{sub:wirtinger_calculus}

@@

% subsection wirtinger_calculus (end)

\subsection{$\cplx$-Linear operator representation} % (fold)
\label{sub:c-linear_operator_representation}

@@

% subsection c-linear_operator_representation (end)

>>>>

% Binary dropout with rate $p \in (0, 1)$ uses $
%   p_\xi
%     = \mathcal{B}\bigl(
%       \{0, \tfrac1{1-p}\}, 1-p
%     \bigr)
% $, whereas in Gaussian dropout $
%   \xi \sim \mathcal{N}(1, \alpha)
% $ for $\alpha = \tfrac{p}{1-p}$.
% This suggests making $\alpha$ a variational parameter
% and optimizing it in \eqref{eq:elbo_general} with an appropriate penalty term. Thus,
%
Variational Dropout assumes fully factorized Gaussian approximate posterior $
  q_\theta(\omega)
    = \prod_j \mathcal{N}(\omega_j \vert\, \mu_j, \alpha_j \mu_j^2)
$ and factorized log-uniform prior $\pi(\omega)$ with $
  \pi(\omega_j) \propto \lvert \omega_j \rvert^{-1}
$. The divergence term in \eqref{eq:elbo} unravels into the following sum:
\begin{equation}  \label{eq:improper-kl-div-real}
  KL(q_\theta \| \pi)
    \propto
      \frac12 \sum_j \mathbb{E}_{\varepsilon \sim \mathcal{N}(0, 1)}
        \log{\Bigl\lvert \tfrac1{\sqrt{\alpha_j}} + \varepsilon \Bigr\rvert^2}
      % \frac12 \mathbb{E}_{\varepsilon \sim \mathcal{N}(0, 1)}
      %   \log{\bigl\lvert 1 + \sqrt{\alpha} \varepsilon \bigr\rvert^2}
      % - \frac12 \log{\alpha}
  \,.
\end{equation}
\citet{kingma_variational_2015} approximate this expression by a non-linear polynomial
regression over $\alpha \in (0, 1)$. \citet{molchanov_variational_2017} refine the
approximation by using a nonlinear regression based on sigmoid and soft-plus.
% see p.6 sec 3.4 of kingma_variational_2015
In appendix~\ref{sec:real-chisq-grad} we verify the value and the derivative of their
approximation against the Monte-Carlo estimate of \eqref{eq:improper-kl-div-real} for $\alpha$
varying over a fine logarithmic grid and the gradient of \eqref{eq:improper-kl-div-real},
for which we obtain an exact expression.
% (!) good for SGVB: gradient-based methods require unbiased gradient estimates
% (in) it is in poor taste to brag about this beign the first time anyone has derived a
% derivative of an intractable function.

The key role in the factorization is played by $\alpha_j$, which reflects the relevance
of the parameter $\omega_j$ it is associated to, by being the ratio of its squared mean
to its variance. Thus, \citet{molchanov_variational_2017} focus on the model sparsification
capabilities of Variational Dropout, optimizing $\alpha_j$ for each individual parameter,
or across groups of parameters for structured sparsity. \citet{kharitonov_variational_2018}
address theoretical issues with improper priors and propose a method based on \textit{
Automatic Relevance Determination} procedure, which falls under \textit{Empirical Bayes}
approach that fits a prior distribution while performing Variational Inference. In this
method the log-uniform factor $\pi(\omega_j)$ is replaced by a proper Gaussian ARD
prior $
  \mathcal{N}(\omega_j \vert\, 0, \tau^{-1}_j)
$ with learnable precision $\tau_j > 0$, \citep{neal_bayesian_1996}. Maximizing
\eqref{eq:elbo} over $\tau$, holding other parameters fixed, yields $
  \tau^*_j = {(\mu_j^2 + \sigma^2_j)}^{-1}
$, whence
\begin{equation}  \label{eq:ard-kl-div-real}
  KL(q_\theta \| \pi)
    = \frac12 \sum_j \log{\bigl(1 + \tfrac1{\alpha_j} \bigr)}
    \,.
\end{equation}

Another contribution of \citep{kingma_variational_2015} is the analysis of the effects of the
\textit{local reparameterization trick} on the variance of the gradient of \eqref{eq:elbo}.
Proposed by \citet{wang_fast_2013} to speed up Gaussian dropout, this trick translates
uncertainty from parameters of the model to intermediate outputs within the network:
the stochasticity of $
  W \in \mathbb{R}^{n\times m}
$ with $
  q(W) = \prod_{ij}
    \mathcal{N}(w_{ij}\vert\, \mu_{ij}, \alpha_{ij} \mu_{ij}^2)
$ in a linear layer is pushed to its output $
  y = b + W^\top x
$,
\begin{equation}  \label{eq:r-gauss-trick}
    q(y) = \prod_i \mathcal{N}\Bigl(
          y_i \big\vert\,
          b_i + \sum_j \mu_{ij} x_j,
          \sum_j \alpha_{ij} \mu_{ij}^2 x_j^2
      \Bigr)
    \,.
\end{equation}
%
\citet{kingma_variational_2015} show, that for the case of fully factorized Gaussian
posterior approximations, using \eqref{eq:r-gauss-trick} decorrelates the estimators
\eqref{eq:elbo} within the mini-batch and makes the gradient estimator $
  \nabla_\theta \tilde{\mathcal{L}}
$ more statistically efficient. Specifically for the problem of selecting relevant parameters
\citet{molchanov_variational_2017} further improve the efficiency of the estimator of the $
  \nabla_\mu \tilde{\mathcal{L}}
$ by introducing \textit{additive noise parameterization}. They revert the $(\mu, \alpha)$
parameterization back to the equivalent $(\mu, \sigma^2)$, since it stabilizes gradients
of SGVB \eqref{eq:elbo}, by rendering the gradient with respect to $\mu$ independent from
the local output noise, injected by \eqref{eq:r-gauss-trick}. The relevance $\alpha$ is
calculated using the ratio $
  \tfrac{\sigma^2}{\mu^2}
$ when needed in the divergence term.

@@

The $\cplx$-variant of the local reparameterization trick utilizes the fact that Gaussian
vectors are closed under affine transformations:
% $\cplx$-Gaussians are closed under affine transformations
\begin{equation}  \label{eq:cn-affine}
  b + A z \sim \mathcal{N}_n^{\cplx}\bigl(
      b + A\mu, A \Gamma A^{\hop}, A C A^\top
    \bigr)
  \,,
\end{equation}
for $A \in \cplx^{n \times m}$ and $b \in \cplx^{n}$. Therefore, if $W \in \cplx^{n\times m}$
is drawn from a fully factorized approximation
\begin{equation}  \label{eq:c-gauss-vi-general}
  W \sim q(W)
    = \prod_{ij} \mathcal{N}^{\cplx} \bigl(
      w_{ij} \vert\, \mu_{ij}, \Sigma_{ij}, C_{ij}
    \bigr)
  \,,
\end{equation}
with $
  \mu, C \in \cplx^{n\times m}
$, $\Sigma \in \real^{n\times m}$, and $
  \lvert C_{ij} \rvert^2 \leq \Sigma_{ij}
$, then for $x \in \cplx^m$ and $b \in \cplx^n$ the vector $y = b + W x$ has independent
components with
\begin{equation}  \label{eq:cplx-gauss-trick}
  y_i
    \sim \mathcal{N}^{\cplx}
      \Bigl(
        % e_i^\top \mu x + b_i,
        b_i + \sum_{j=1}^m \mu_{ij} x_j,
        \, \sum_{j=1}^m \Sigma_{ij} \lvert x_j \rvert^2,
        \, \sum_{j=1}^m C_{ij} x_j^2
      \Bigr)
    \,.
\end{equation}
The trick requires three operations, i.e. $b + \mu x$, $\Sigma \lvert x \rvert^2$ and
$C x^2$ with the complex modulus and square applied elementwise, and can be applied to
any layer, the output of which depends linearly on its parameters, such as convolutional,
affine, and bilinear transformations ($
  (x, z) \mapsto x^\top W^{(j)} z + b_j
$). Similar to $\real$ case, Variational Dropout for $\cplx$ convolutions draws independent
realizations of $W$ for each spatial patch in the input \citep{molchanov_variational_2017}.
This provides faster computations and better statistical efficiency of the SGVB gradient
estimator stemming from decorrelated gradient estimates from overlapping patches
\citep{kingma_variational_2015}, allowing \eqref{eq:cplx-gauss-trick} to leverage $\cplx$
convolutions of the relation and variance kernels with elementwise complex squares $x^2$
and amplitudes $\lvert x \rvert^2$.
% Weight sharing is essentially pushed to shared variational parameters $\theta$ in the approximation $q_\theta$.
% A convolution is a matrix product of $W$, unrolled into a toeplitz matrix, and im-to-col
% flattened intput $x$

@@

\begin{figure}[!t]
  \centering
  \begin{subfigure}[b]{1.\columnwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=\columnwidth]{figure__musicnet__threshold.pdf}
  \end{subfigure}
  \caption{%
    Test split performance and compression rate for a $\cplx$-valued net on MusicNet.
  }
  \label{fig:hist__and__threshold__tradeoff}
\end{figure}

@@

Shaded horizontal bands reflect the spread of the performance of the uncompressed network
after ``dense'' stage. Each point represents a precision-compression value attained by the
network after ``fine-tune'' stage. The end of each point's tail represents the performance
gain or loss from running the ``fine-tune'' stage.
%
We make a couple of observations based on the results of these plots. First, \texttt{fft}
features perform on par with raw colour channel data in the convolutional networks across most
compression rates, but require high compression rate to make wide shallow dense network work
as well. The upward trend manifests itself in MNIST and Fashion MNIST experiments as well
(see appendix~\ref{sec:mnist_like_experiments}). Finally, overall $\cplx$ variational dropout
methods seem to compress networks adequately well without much loss in performance.

% a couple of plots from MNIST and Fashion-MNIST
\begin{figure}[!t]
  \centering
  \begin{subfigure}[b]{1.\columnwidth}  % imcl2019-style swears at this
    \centering
    % \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/legacy__VD__fashionmnist__fft__-0.5.pdf}
    \includegraphics[width=0.8\columnwidth]{figure__mnist-like__trade-off/legacy__VD__kmnist__fft__-0.5.pdf}
    % \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/VD__kmnist__fft__-0.5.pdf}
  \end{subfigure} \\%
  % \hfill
  \begin{subfigure}[b]{1.\columnwidth}  % imcl2019-style swears at this
    \centering
    % \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/legacy__VD__fashionmnist__raw__-0.5.pdf}
    \includegraphics[width=0.8\columnwidth]{figure__mnist-like__trade-off/legacy__VD__kmnist__raw__-0.5.pdf}
    % \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/VD__kmnist__raw__-0.5.pdf}
  \end{subfigure} \\%
  \begin{subfigure}[b]{1.\columnwidth}  % imcl2019-style swears at this
    \centering
    % \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/legacy__VD__mnist__fft__-0.5.pdf}
    \includegraphics[width=0.8\columnwidth]{figure__mnist-like__trade-off/legacy__VD__emnist_letters__fft__-0.5.pdf}
    % \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/ARD__kmnist__fft__-0.5.pdf}
  \end{subfigure} \\%
  % \hfill
  \begin{subfigure}[b]{1.\columnwidth}  % imcl2019-style swears at this
    \centering
    % \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/legacy__VD__mnist__raw__-0.5.pdf}
    \includegraphics[width=0.8\columnwidth]{figure__mnist-like__trade-off/legacy__VD__emnist_letters__raw__-0.5.pdf}
    % \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/VD__emnist_letters__raw__-0.5.pdf}
  \end{subfigure}
  \caption{%
    The compression-accuracy trade-off on KMNIST and the letters of the Extended MNIST datasets.
    (\textit{top}) \texttt{fft} features, (\textit{bottom}) \texttt{raw} features.
  }
  \label{fig:mnist-like__trade-off}
\end{figure}

@@

% compare compressed cplx-vgg against real-vgg
\begin{figure}[!t]
  \centering
  \begin{subfigure}[b]{1.\columnwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=\columnwidth]{figure__cifar__trade-off/legacy__augmentedcifar10__raw__-0.5.pdf}
  \end{subfigure}
  \caption{%
    Compression-accuracy frontier for $\real$ and $\tfrac12 \cplx$ versions of VGG16 on CIFAR10.
  }
  \label{fig:figure__cifar10__trade-off}
\end{figure}

@@

\begin{figure}[!t]
  \centering
  \begin{subfigure}[b]{1.\columnwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=\columnwidth]{figure__musicnet__trade-off/paper__musicnetram__fft__-0.5.pdf}
  \end{subfigure}
  \caption{%
    Performance-compression trade-off using \textbf{\color{blue} VD} and \textbf{\color{orange} ARD}.
    The \textbf{\color{pink} version} of the network with kernel $3$ in the first convolution is
    compressed with VD only.
  }
  \label{fig:musicnet__trade-off}
\end{figure}

@@

% \clearpage

@@

% \clearpage

\appendix
\onecolumn

\section{Complex-valued local reparameterization} % (fold)
\label{sec:complex_valued_local_reparameterization}

@@

% section complex_valued_local_reparameterization (end)

\section{Gradient of the KL-divergence in $\real$ case} % (fold)
\label{sec:real-chisq-grad}  % gradient_of_the_kl_divergence_in_R_case

@@

% section real-chisq-grad (end)

\section{MNIST-like experiments} % (fold)
\label{sec:mnist_like_experiments}

@@

% section mnist_like_experiments (end)

@@

\section{CIFAR10 experiments} % (fold)
\label{sec:cifar_experiments}

@@

% section cifar_experiments (end)

\section{Backpropagation through $\cplx$-networks} % (fold)
\label{sub:wirtinger_calculus}

@@

% section wirtinger_calculus (end)

\section{$\cplx$-Linear operator representation} % (fold)
\label{sec:c-linear_operator_representation}

@@

% section c-linear_operator_representation (end)
